---
title: "Home"
---

Welcome the Terrestrial Ecosystem Research Network ([TERN](https://www.tern.org.au)) Ecological Forecasting Challenge dashboard, hosted by the Ecological Forecasting Initiative ([EFI](https://ecoforecast.org))

This site provides instructions for participation, visualizations of forecast submissions, and a catalog of all submitted forecasts. It is rendered daily using GitHub Actions.

```{r setup, include=FALSE, echo=FALSE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE)
library(dplyr)
library(arrow)
library(bslib)
library(bsicons)
```

```{r}
combined <- arrow::open_dataset("../cache/parquet/")

n_forecasts <- combined |> distinct(model_id, reference_datetime) |> collect() |> nrow()
n_models <- combined |> distinct(model_id) |> collect() |> nrow()

last_updated <- Sys.Date()

```

Page last updated on `r Sys.Date()`

```{r eval = FALSE}

layout_column_wrap(
  width = "250px",
  value_box(
    title = "Total forecasts submitted to the EFI TERN Challenge", 
    value = n_forecasts,
    showcase = bs_icon("graph-up"),
    theme_color = "success" 
  ),
  value_box(
    title = "Unique models submitted to the EFI TERN Challenge", 
    value = n_models,
    showcase = bs_icon("pie-chart")
  )
)

```

## Submit a forecast!

EFI-TERN Challenge currently has one open challenge theme! Browse the current forecasts or submit your own.

------------------------------------------------------------------------

Data was sourced from Terrestrial Ecosystem Research Network (TERN) infrastructure, which is enabled by the Australian Government\'s *National Collaborative Research Infrastructure Strategy* (NCRIS).

This material is based upon work supported by the National Science Foundation under Grant DEB-1926388. Any opinions, findings, and conclusions or recommendations expressed in this material are those of the author(s) and do not necessarily reflect the views of the National Science Foundation.
