---
title: "home"
---

Welcome the [EFI](https://ecoforecast.org) NEON Forecast Challenge Dashboard.

This site provides daily updates to visualize recent scores of all forecasts submitted to the challenge. This site is generated using [quarto](https://quarto.org) and should be simple to customize for users familiar with RMarkdown. It is rendered daily using GitHub Actions.



```{r setup, include=FALSE, echo=FALSE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE)
library(tidyverse)
library(arrow)
library(bslib)
library(bsicons)
```


```{r}
combined <- arrow::open_dataset("cache/parquet/")

n_forecasts <- combined |> distinct(model_id, reference_datetime) |> collect() |> nrow()
n_models <- combined |> distinct(model_id) |> collect() |> nrow()

last_updated <- Sys.Date()

```

```{r include = FALSE}

layout_column_wrap(
  width = "250px",
  value_box(
    title = "Total forecasts submitted to the EFI Challenge", 
    value = n_forecasts,
    showcase = bs_icon("graph-up"),
    theme_color = "success" 
  ),
  value_box(
    title = "Unique models submitted to the EFI Challenge", 
    value = n_models,
    showcase = bs_icon("pie-chart")
  )
)

```


## Submit a forecast!

EFI currently has five open challenge themes! 
Browse the current forecasts or submit your own. Learn more about the [current challenges](https://projects.ecoforecast.org/neon4cast-docs).





------------------------------------------------------------------------

This material is based upon work supported by the National Science Foundation under Grant DBI-1942280. Any opinions, findings, and conclusions or recommendations expressed in this material are those of the author(s) and do not necessarily reflect the views of the National Science Foundation.
