---
title: "Instructions"
---

**What:** Net ecosystem exchange of CO2 and evapotranspiration in terrestrial ecosystems

**Where**: 3 TERN sites across Australia

**When**: Daily forecasts for at least 30-days in the future are accepted at any time. New forecast submissions are accepted daily. The only requirement is that submissions are predictions of the future at the time the forecast is submitted.

**Why:** Carbon and water cycling are fundamental for climate and water regulation services provided by ecosystems

**Who**: Open to any individual or team that registers

**How**: PENDING

The video below is an overview of the Terrestrial Carbon and Water Fluxes Challenge that was recorded for the [2021 Early Career Annual Meeting](https://ecoforecast.org/ecological-forecasting-early-career-annual-meeting/){target="_blank"}

<iframe width="560" height="315" src="https://www.youtube.com/embed/WmFsACm-TMk" title="YouTube video player" frameborder="0" allow="accelerometer; autoplay; clipboard-write; encrypted-media; gyroscope; picture-in-picture" allowfullscreen>

</iframe>

We held a Q&A session on January 22, 2021. You can find a recording from that session [HERE](https://www.youtube.com/watch?v=3rOVlAX9YH8&feature=youtu.be){target="_blank"}.

```{r echo = FALSE, message = FALSE}
library("tidyverse")
```

## Overview

The exchange of water and carbon dioxide between the atmosphere and the land is akin to earth's terrestrial ecosystems breathing rate and lung capacity. One of the best ways to monitor changes in the amount of carbon and water in an ecosystem is the eddy-covariance method. This method observes the net amount of carbon and water entering and exiting ecosystems at half-hourly timesteps, which is important because it can provide information on ecosystem processes such as photosynthesis, respiration, and transpiration, their sensitivities to ongoing climate and land use change, and greenhouse gas budgets for carbon accounting and natural climate solutions. Forecasts of carbon uptake and release along with water use can provide insights into future production of food, fiber, timber, and carbon credits. Additionally, forecasts will highlight the influence that stress and disturbance have on carbon and water cycling.

## Challenge

This forecasting challenge asks teams to forecast net ecosystem exchange of carbon dioxide (NEE) and latent heat flux of evapotranspiration (LE) across 3 TERN sites with differing climates. Forecasts  daily time step over the next 30-days. Weather forecasts from NOAA Global Ensemble Forecast System are provided to use as model drivers (if forecasting model uses meteorological inputs). Forecasts can be submitted daily

Teams are asked to submit their forecast of measured NEON NEE and LE, along with uncertainty estimates and metadata. Any existing NEE and LE may be used to build and improve the models used to generate forecasts. Other data can be used so long as they are not from the month being forecast and the data are made publicly available (minimum of URL, but ideally a script) and accessible to all teams in the challenge.

## Data: Targets

The challenge uses the following TERN data products:

INSERT

A file with previously released TERN data that has been processed into "targets" is provided below. The same processing will be applied to new data that are used for forecast evaluation. 
### Net ecosystem exchange

**Definition**

Net ecosystem exchange (NEE) is the net movement of carbon dioxide from the atmosphere to the ecosystem. At the 30-minute time resolution it is reported as $\mu$mol CO<sub>2</sub> m<sup>-2</sup> s<sup>-1</sup>. At the daily time resolution it is reported as g C m<sup>-2</sup> day<sup>-1</sup>. Negative values correspond to an ecosystem absorbing CO<sup>2</sup> from the atmosphere, positive values correspond to an ecosystem emitting CO<sub>2</sub> to the atmosphere.

**Motivation**

NEE quantifies the net exchange of CO<sub>2</sub> between the ecosystem and the atmosphere over that 30-minute or daily time period. Assessing skill at predicting 1/2 hourly - sub daily measurements provides more insight into ability to capture diel processes. The diel curve contains information on how plants and soil immediately respond to variations in meteorology.

Making daily predictions will allow us to rapidly assess skill and provide information in a timeframe pertinent to inform and implement natural resource management. It also allows for models that do not produce sub-daily estimates to participate

### Latent heat flux

**Definition**

Latent heat flux is the movement of water as water vapor from the ecosystem to the atmosphere. It is reported as W m<sup>-2</sup> (equivalent to J m<sup>-2</sup> s<sup>-1</sup>). At the daily time resolution it is reported as mean W m<sup>-2</sup>. Positive values correspond to a transfer of water vapor from the ecosystem to the atmosphere.

**Motivation**

Latent heat measures the water loss from an ecosystem to the atmosphere through evapotranspiration (transpiration through plants + evaporation from surfaces).

Forecasting latent heat (evapotranspiration) can provide insights to water stress for plants and the efficiency that plants are using water relative to NEE, and to the amount of liquid water remaining in the soil for soil moisture forecasting

### Focal sites

Information on the sites can be found here:

```{r message = FALSE}
site_data <- readr::read_csv("https://raw.githubusercontent.com/eco4cast/tern4cast/main/tern_field_site_metadata.csv") |> 
  dplyr::filter(!is.na(data_url))
```

### target data calculation

To create the data for evaluation (and training) for NEE and LE we extract NEE and LE that pass the turbulence quality control flags (`qfqm.fluxCo2.turb.qfFinl` = 0 ) provided by NEON and has flux values between -50 and 50 umol CO2 m<sup>-2</sup> s<sup>-1</sup>.

The table with the half-hour NEE and LE has the following columns

-   `datetime`: YYYY-MM-DD HH:MM for the start of the 30-minute period in UTC\
-   `site_id`: NEON site code (e.g., BART)\
-   `variable`: `nee` (umol CO2 m<sup>-2</sup> s<sup>-1</sup>) or `le` W m<sup>-2</sup>\
-   `observed`: value for variable

To evaluate daily flux forecasts, we select only days with at least 24 of 48 half hours that pass the quality control flags. For these days, we average the half-hours and convert carbon to daily units (gC/m2/day). The daily data table has the following columns.

-   `datetime`: YYYY-MM-DD (the day is determined using UTC time)\
-   `site_id`: NEON site code (e.g., BART)\
-   `variable`: `nee` (g C m<sup>-2</sup> day<sup>-1</sup>) or `le` (W m<sup>-2</sup>)
-   `observation`: value for variable

Here is the download link and format of the `terrestrial_daily` target file

```{r message = FALSE}
readr::read_csv("https://data.ecoforecast.org/tern4cast-targets/terrestrial_daily/terrestrial_daily-targets.csv.gz", guess_max = 1e6) |> 
  na.omit()
```
## Timeline

Forecasts for a minimum of 30 days can be submitted daily. New forecasts can be submitted daily as new weather forecasts and observations (e.g., NEE) become available. The key is that submissions are predictions of the future.

Daily submissions are allowed and encouraged as new observations and weather forecasts become available, therefore the automation of forecast generation may be ideal. There are many ways to automate scripts that are written to download observations and metreology drivers, generate forecasts, and submit forecasts. Two tools that many have used are cron jobs (see the R package [cronR](https://cran.r-project.org/web/packages/cronR/index.html){target="_blank"}) that execute tasks at user specifics times and [github actions](https://youtu.be/dMrUlXi4_Bo){target="_blank"}.

Cron jobs work on unix and mac systems. An example of a script that executes a cron job using R can be found [here](https://github.com/eco4cast/neon4cast-phenology/blob/master/cron_automation.R){target="_blank"}.

## Flux data latency

PENDING

## Submissions

The required names for forecasted variables: `nee`, and `le`.

The required time unit: `YYYY-MM-DD`

ADDING MORE HERE

## Meterological inputs for modeling

PENDING

## Useful functions

PENDING

## Null models

Two null models are automatically generated each day - these are simple baseline models. The persistence null model uses the most recent measurement of nee or le and predicts that the values will be constant in the future. The climatology null model forecasts that the nee or lee will be equal to the historical mean of that day of year. We apply both the persistence and climatology model to the daily fluxes.

Code for the daily persistence null model can be found [here](https://github.com/eco4cast/neon4cast-baselines/blob/main/terrestrial_daily_persistance.R){target="\"_blank"}

Code for the daily climatology null model can be found [here](https://github.com/eco4cast/neon4cast-baselines/blob/main/terrestrial_daily_climatology.R){target="_blank"}

## FAQ

PENDING

## Design team

Terrestrial Ecosystem Research Network [(TERN)](https://www.tern.org.au/){target="_blank"} has been involved in the design of the challenge.
````
