---
title: "Terrestrial"
---

```{r, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message=FALSE, warning=FALSE)
```

```{r setup}
library(ggiraph)
library(patchwork)
library(tidyverse)
library(neon4cast)
library(score4cast)
library(glue)
source("R/plot-utils.R")
score4cast::ignore_sigpipe()


```

# Daily averages

```{r }
theme <- "terrestrial_daily"
cutoff <- as.character(Sys.Date() - 30)
combined <- arrow::open_dataset(glue("cache/parquet/{theme}")) |>
  filter(date >= cutoff) |> collect()

```





```{r}
sites <- combined |> distinct(site_id) |> collect() |> slice_head(n= 6) |> pull(site_id)
## with at least n observations to compare!
n_data <- 10
who <- combined |> filter(!is.na(observation)) |> summarise(has_data = max(reference_datetime)) |> collect()
ref <- as.character ( as.Date(who$has_data[[1]]) - n_data )
ex <- combined |> filter(reference_datetime == ref, site_id %in% sites) 

```

## Most recent forecasts

Below is the latest forecasts for which we have at least 10 observations. Mouse over to see the team id, scroll to zoom.

::: panel-tabset
## Latent evaporation

```{r}
ex |> filter(reference_datetime == ref, variable == "le") |> forecast_plots()
```

## CO2 Flux

Net ecosystem exchange of CO2 (NEE)

```{r}
ex |> filter(reference_datetime == ref, variable == "nee") |> forecast_plots()
```

## vswc

```{r}
 ex |> filter(reference_datetime == ref, variable == "vswc") |> forecast_plots()
```
:::


## Leaderboard

Average skill scores of each model across all sites.  
Scores are shown by reference date and forecast horizon (in days).  
Scores are averaged across all submissions of the model with a given horizon or a given `reference_datetime` out of submissions made since cutoff date.

```{r include=TRUE}
cutoff
```

::: panel-tabset
## Latent evaporation

```{r}
leaderboard_plots(combined, "le")
```

## CO2 flux

```{r}
leaderboard_plots(combined, "nee")
```

## vswc

(no data)

```{r}
# leaderboard_plots(combined, "vswc")
```
:::
